### 2014-10-06 LaTeX/mCitySimPlot.tex
updating plots

% Created by tikzDevice version 0.7.0 on 2014-09-23 11:39:59
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 39.69, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 57.05,110.46) --
	( 62.08,112.14) --
	( 67.11,113.83) --
	( 72.14,115.51) --
	( 77.17,117.20) --
	( 82.20,118.88) --
	( 87.23,120.57) --
	( 92.27,122.25) --
	( 97.30,123.94) --
	(102.33,125.62) --
	(107.36,127.30) --
	(112.39,128.99) --
	(117.42,130.67) --
	(122.45,132.36) --
	(127.49,134.04) --
	(132.52,135.73) --
	(137.55,137.41) --
	(142.58,139.10) --
	(147.61,140.78) --
	(152.64,142.47) --
	(157.67,144.15) --
	(162.71,145.84) --
	(167.74,147.52) --
	(172.77,149.20) --
	(177.80,150.89) --
	(182.83,152.57) --
	(187.86,154.26) --
	(192.89,155.94) --
	(197.93,157.63) --
	(202.96,159.31) --
	(207.99,161.00) --
	(213.02,162.68) --
	(218.05,164.37) --
	(223.08,166.05) --
	(228.12,167.74) --
	(233.15,169.42) --
	(238.18,171.11) --
	(243.21,172.79) --
	(248.24,174.47) --
	(253.27,176.16) --
	(258.30,177.84) --
	(263.34,179.53) --
	(268.37,181.21) --
	(273.40,182.90) --
	(278.43,184.58) --
	(283.46,186.27) --
	(288.49,187.95) --
	(293.52,189.64) --
	(298.56,191.32) --
	(303.59,193.01) --
	(308.62,194.69) --
	(313.65,196.38) --
	(318.68,198.06) --
	(323.71,199.74) --
	(328.74,201.43) --
	(333.78,203.11) --
	(338.81,204.80) --
	(343.84,206.48) --
	(348.87,208.17) --
	(353.90,209.85) --
	(358.93,211.54) --
	(363.96,213.22) --
	(369.00,214.91) --
	(374.03,216.59) --
	(379.06,218.28) --
	(384.09,219.96) --
	(389.12,221.65) --
	(394.15,223.33) --
	(399.18,225.01) --
	(404.22,226.70);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 57.05,174.43) --
	( 62.08,174.80) --
	( 67.11,175.43) --
	( 72.14,175.95) --
	( 77.17,176.45) --
	( 82.20,177.01) --
	( 87.23,177.60) --
	( 92.27,178.07) --
	( 97.30,178.83) --
	(102.33,179.63) --
	(107.36,180.19) --
	(112.39,180.68) --
	(117.42,181.22) --
	(122.45,181.91) --
	(127.49,182.61) --
	(132.52,183.22) --
	(137.55,183.85) --
	(142.58,184.72) --
	(147.61,185.27) --
	(152.64,185.85) --
	(157.67,186.68) --
	(162.71,187.40) --
	(167.74,188.19) --
	(172.77,188.79) --
	(177.80,189.72) --
	(182.83,190.53) --
	(187.86,191.58) --
	(192.89,192.32) --
	(197.93,193.15) --
	(202.96,194.08) --
	(207.99,195.20) --
	(213.02,196.17) --
	(218.05,197.04) --
	(223.08,198.12) --
	(228.12,199.15) --
	(233.15,200.19) --
	(238.18,201.29) --
	(243.21,202.47) --
	(248.24,203.82) --
	(253.27,205.19) --
	(258.30,206.48) --
	(263.34,207.77) --
	(268.37,209.20) --
	(273.40,210.73) --
	(278.43,212.20) --
	(283.46,213.76) --
	(288.49,215.30) --
	(293.52,216.81) --
	(298.56,218.76) --
	(303.59,220.71) --
	(308.62,222.73) --
	(313.65,224.51) --
	(318.68,226.51) --
	(323.71,228.57) --
	(328.74,230.64) --
	(333.78,232.65) --
	(338.81,234.73) --
	(343.84,236.98) --
	(348.87,239.31) --
	(353.90,241.60) --
	(358.93,243.92) --
	(363.96,246.40) --
	(369.00,248.74) --
	(374.03,251.08) --
	(379.06,253.40) --
	(384.09,255.89) --
	(389.12,258.42) --
	(394.15,260.84) --
	(399.18,263.30) --
	(404.22,265.99) --
	(404.22,186.70) --
	(399.18,185.91) --
	(394.15,185.08) --
	(389.12,184.30) --
	(384.09,183.58) --
	(379.06,182.70) --
	(374.03,181.87) --
	(369.00,180.89) --
	(363.96,179.93) --
	(358.93,178.91) --
	(353.90,178.04) --
	(348.87,176.86) --
	(343.84,175.89) --
	(338.81,174.74) --
	(333.78,173.45) --
	(328.74,172.28) --
	(323.71,171.02) --
	(318.68,169.43) --
	(313.65,167.97) --
	(308.62,166.54) --
	(303.59,165.18) --
	(298.56,163.70) --
	(293.52,162.08) --
	(288.49,160.29) --
	(283.46,158.60) --
	(278.43,156.91) --
	(273.40,155.18) --
	(268.37,153.23) --
	(263.34,151.42) --
	(258.30,149.61) --
	(253.27,147.65) --
	(248.24,145.45) --
	(243.21,143.23) --
	(238.18,141.02) --
	(233.15,138.72) --
	(228.12,136.35) --
	(223.08,133.80) --
	(218.05,131.34) --
	(213.02,128.83) --
	(207.99,126.45) --
	(202.96,124.00) --
	(197.93,121.57) --
	(192.89,119.03) --
	(187.86,116.41) --
	(182.83,113.90) --
	(177.80,111.23) --
	(172.77,108.70) --
	(167.74,105.98) --
	(162.71,103.34) --
	(157.67,100.79) --
	(152.64, 98.10) --
	(147.61, 95.49) --
	(142.58, 92.64) --
	(137.55, 89.85) --
	(132.52, 87.02) --
	(127.49, 84.25) --
	(122.45, 81.44) --
	(117.42, 78.59) --
	(112.39, 75.96) --
	(107.36, 73.32) --
	(102.33, 70.44) --
	( 97.30, 67.62) --
	( 92.27, 64.83) --
	( 87.23, 61.80) --
	( 82.20, 58.96) --
	( 77.17, 56.21) --
	( 72.14, 53.52) --
	( 67.11, 50.65) --
	( 62.08, 47.79) --
	( 57.05, 45.08) --
	cycle;
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.50] ( 57.05,165.69) --
	( 62.08,166.26) --
	( 67.11,166.92) --
	( 72.14,167.65) --
	( 77.17,168.34) --
	( 82.20,169.03) --
	( 87.23,169.66) --
	( 92.27,170.38) --
	( 97.30,171.07) --
	(102.33,171.75) --
	(107.36,172.44) --
	(112.39,173.12) --
	(117.42,173.84) --
	(122.45,174.45) --
	(127.49,175.12) --
	(132.52,175.81) --
	(137.55,176.59) --
	(142.58,177.35) --
	(147.61,178.25) --
	(152.64,179.27) --
	(157.67,180.18) --
	(162.71,181.11) --
	(167.74,181.96) --
	(172.77,182.76) --
	(177.80,183.71) --
	(182.83,184.54) --
	(187.86,185.47) --
	(192.89,186.43) --
	(197.93,187.51) --
	(202.96,188.46) --
	(207.99,189.58) --
	(213.02,190.58) --
	(218.05,191.75) --
	(223.08,192.84) --
	(228.12,194.00) --
	(233.15,195.12) --
	(238.18,196.45) --
	(243.21,197.65) --
	(248.24,199.02) --
	(253.27,200.34) --
	(258.30,201.75) --
	(263.34,203.21) --
	(268.37,204.61) --
	(273.40,206.24) --
	(278.43,207.82) --
	(283.46,209.30) --
	(288.49,210.93) --
	(293.52,212.69) --
	(298.56,214.53) --
	(303.59,216.36) --
	(308.62,218.21) --
	(313.65,220.05) --
	(318.68,222.00) --
	(323.71,224.00) --
	(328.74,225.95) --
	(333.78,227.98) --
	(338.81,230.07) --
	(343.84,232.25) --
	(348.87,234.41) --
	(353.90,236.60) --
	(358.93,238.76) --
	(363.96,240.91) --
	(369.00,243.13) --
	(374.03,245.40) --
	(379.06,247.74) --
	(384.09,250.09) --
	(389.12,252.61) --
	(394.15,255.21) --
	(399.18,257.56) --
	(404.22,259.93) --
	(404.22,192.89) --
	(399.18,192.12) --
	(394.15,191.18) --
	(389.12,190.22) --
	(384.09,189.28) --
	(379.06,188.36) --
	(374.03,187.32) --
	(369.00,186.30) --
	(363.96,185.20) --
	(358.93,184.18) --
	(353.90,182.99) --
	(348.87,181.90) --
	(343.84,180.64) --
	(338.81,179.59) --
	(333.78,178.30) --
	(328.74,176.91) --
	(323.71,175.49) --
	(318.68,174.05) --
	(313.65,172.59) --
	(308.62,171.06) --
	(303.59,169.50) --
	(298.56,167.92) --
	(293.52,166.28) --
	(288.49,164.66) --
	(283.46,162.97) --
	(278.43,161.38) --
	(273.40,159.49) --
	(268.37,157.55) --
	(263.34,155.74) --
	(258.30,153.81) --
	(253.27,151.84) --
	(248.24,149.82) --
	(243.21,147.69) --
	(238.18,145.73) --
	(233.15,143.60) --
	(228.12,141.48) --
	(223.08,139.15) --
	(218.05,136.75) --
	(213.02,134.58) --
	(207.99,132.15) --
	(202.96,129.81) --
	(197.93,127.34) --
	(192.89,124.90) --
	(187.86,122.54) --
	(182.83,119.97) --
	(177.80,117.68) --
	(172.77,115.15) --
	(167.74,112.73) --
	(162.71,110.22) --
	(157.67,107.87) --
	(152.64,105.34) --
	(147.61,102.80) --
	(142.58,100.16) --
	(137.55, 97.55) --
	(132.52, 94.94) --
	(127.49, 92.32) --
	(122.45, 89.72) --
	(117.42, 87.08) --
	(112.39, 84.45) --
	(107.36, 81.80) --
	(102.33, 79.16) --
	( 97.30, 76.57) --
	( 92.27, 74.01) --
	( 87.23, 71.42) --
	( 82.20, 68.63) --
	( 77.17, 65.97) --
	( 72.14, 63.37) --
	( 67.11, 60.74) --
	( 62.08, 58.05) --
	( 57.05, 55.38) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	( 39.69,277.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 52.86) {3.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57, 96.58) {3.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,140.30) {3.9};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,184.02) {4.0};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,227.74) {4.1};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 32.57,271.45) {4.2};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 39.69, 34.03) --
	(421.57, 34.03);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 40.56, 20.31) {0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at ( 90.87, 20.31) {1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (141.19, 20.31) {2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (191.50, 20.31) {3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (241.82, 20.31) {4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (292.13, 20.31) {5};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (342.45, 20.31) {6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.96] at (392.76, 20.31) {7};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (230.63,  4.82) {Ln(Min. City Dist.)$_{t}$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

>>>>

% Created by tikzDevice version 0.7.0 on 2014-10-06 19:44:41
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (433.62,289.08);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (433.62,289.08);
\definecolor[named]{drawColor}{rgb}{1.00,1.00,1.00}
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round,fill=fillColor] (  0.00,  0.00) rectangle (433.62,289.08);
\end{scope}
\begin{scope}
\path[clip] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{fillColor}{rgb}{1.00,1.00,1.00}

\path[fill=fillColor] ( 35.42, 34.03) rectangle (421.57,277.03);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 52.97,106.37) --
	( 61.01,109.04) --
	( 65.48,110.52) --
	( 65.62,110.57) --
	( 79.64,115.23) --
	( 88.50,118.17) --
	( 94.41,120.14) --
	( 97.84,121.27) --
	(104.50,123.49) --
	(110.01,125.32) --
	(113.94,126.62) --
	(116.56,127.49) --
	(124.94,130.28) --
	(160.01,141.93) --
	(160.15,141.97) --
	(163.56,143.10) --
	(164.50,143.42) --
	(175.08,146.93) --
	(177.68,147.80) --
	(185.12,150.27) --
	(195.04,153.56) --
	(195.05,153.57) --
	(199.79,155.14) --
	(200.09,155.24) --
	(201.70,155.77) --
	(202.42,156.01) --
	(203.15,156.26) --
	(203.24,156.29) --
	(203.92,156.51) --
	(204.08,156.56) --
	(205.70,157.10) --
	(211.30,158.97) --
	(213.02,159.54) --
	(213.22,159.60) --
	(213.28,159.62) --
	(214.88,160.15) --
	(219.39,161.65) --
	(219.87,161.81) --
	(224.51,163.35) --
	(226.38,163.97) --
	(226.89,164.14) --
	(228.22,164.58) --
	(229.80,165.11) --
	(230.53,165.35) --
	(231.54,165.69) --
	(232.29,165.94) --
	(232.55,166.02) --
	(232.60,166.04) --
	(233.03,166.18) --
	(236.50,167.34) --
	(238.44,167.98) --
	(239.50,168.33) --
	(240.76,168.75) --
	(242.87,169.45) --
	(243.82,169.77) --
	(244.87,170.11) --
	(245.90,170.46) --
	(247.14,170.87) --
	(247.15,170.87) --
	(248.00,171.16) --
	(248.59,171.35) --
	(249.15,171.54) --
	(249.91,171.79) --
	(250.14,171.87) --
	(250.71,172.06) --
	(251.21,172.22) --
	(251.61,172.35) --
	(251.88,172.44) --
	(252.52,172.66) --
	(252.98,172.81) --
	(253.12,172.85) --
	(253.36,172.94) --
	(254.91,173.45) --
	(255.02,173.49) --
	(256.32,173.92) --
	(258.61,174.68) --
	(260.03,175.15) --
	(260.14,175.19) --
	(260.80,175.41) --
	(261.97,175.79) --
	(262.19,175.87) --
	(262.48,175.96) --
	(262.99,176.14) --
	(264.29,176.57) --
	(264.50,176.64) --
	(264.53,176.65) --
	(264.97,176.79) --
	(266.10,177.17) --
	(266.13,177.18) --
	(266.44,177.28) --
	(267.28,177.56) --
	(267.71,177.70) --
	(268.38,177.92) --
	(269.11,178.17) --
	(269.74,178.38) --
	(269.87,178.42) --
	(271.02,178.80) --
	(271.10,178.83) --
	(271.68,179.02) --
	(272.40,179.26) --
	(272.79,179.39) --
	(273.63,179.67) --
	(274.52,179.96) --
	(275.28,180.22) --
	(275.59,180.32) --
	(276.13,180.50) --
	(276.31,180.56) --
	(276.77,180.71) --
	(277.30,180.89) --
	(277.98,181.12) --
	(278.04,181.13) --
	(278.45,181.27) --
	(279.17,181.51) --
	(279.30,181.55) --
	(279.52,181.62) --
	(279.66,181.67) --
	(279.69,181.68) --
	(280.15,181.83) --
	(280.53,181.96) --
	(280.72,182.02) --
	(281.20,182.18) --
	(281.36,182.24) --
	(281.45,182.27) --
	(282.80,182.71) --
	(283.05,182.80) --
	(283.89,183.08) --
	(283.98,183.11) --
	(284.07,183.14) --
	(284.62,183.32) --
	(284.86,183.40) --
	(285.03,183.46) --
	(285.13,183.49) --
	(286.00,183.78) --
	(286.57,183.97) --
	(286.59,183.98) --
	(287.25,184.19) --
	(287.81,184.38) --
	(288.54,184.62) --
	(288.59,184.64) --
	(289.22,184.85) --
	(289.76,185.03) --
	(290.76,185.36) --
	(290.86,185.39) --
	(291.20,185.51) --
	(291.32,185.54) --
	(291.81,185.71) --
	(291.88,185.73) --
	(292.21,185.84) --
	(292.36,185.89) --
	(292.42,185.91) --
	(292.49,185.93) --
	(292.51,185.94) --
	(292.62,185.98) --
	(293.21,186.17) --
	(293.91,186.41) --
	(295.25,186.85) --
	(295.45,186.92) --
	(295.51,186.94) --
	(295.93,187.08) --
	(295.99,187.10) --
	(296.10,187.13) --
	(296.47,187.26) --
	(296.65,187.32) --
	(296.99,187.43) --
	(297.01,187.43) --
	(297.04,187.45) --
	(297.05,187.45) --
	(297.09,187.46) --
	(297.13,187.47) --
	(297.22,187.51) --
	(297.31,187.53) --
	(297.31,187.53) --
	(297.71,187.67) --
	(297.96,187.75) --
	(298.34,187.88) --
	(298.57,187.95) --
	(299.04,188.11) --
	(300.58,188.62) --
	(300.69,188.66) --
	(301.32,188.87) --
	(302.10,189.13) --
	(302.23,189.17) --
	(302.50,189.26) --
	(302.82,189.36) --
	(302.98,189.42) --
	(303.49,189.59) --
	(303.87,189.71) --
	(304.04,189.77) --
	(304.05,189.77) --
	(304.17,189.82) --
	(304.21,189.83) --
	(304.88,190.05) --
	(305.44,190.24) --
	(305.52,190.26) --
	(305.61,190.29) --
	(305.86,190.37) --
	(306.19,190.49) --
	(306.32,190.53) --
	(307.91,191.06) --
	(307.96,191.07) --
	(308.47,191.24) --
	(308.57,191.27) --
	(309.22,191.49) --
	(309.44,191.56) --
	(309.51,191.59) --
	(309.67,191.64) --
	(310.00,191.75) --
	(310.25,191.83) --
	(310.76,192.00) --
	(310.92,192.06) --
	(311.04,192.09) --
	(311.16,192.14) --
	(311.41,192.22) --
	(311.41,192.22) --
	(311.44,192.23) --
	(311.54,192.26) --
	(311.68,192.31) --
	(311.68,192.31) --
	(311.88,192.38) --
	(312.22,192.49) --
	(312.92,192.72) --
	(313.12,192.79) --
	(313.27,192.84) --
	(313.53,192.93) --
	(313.83,193.02) --
	(314.24,193.16) --
	(314.31,193.18) --
	(314.45,193.23) --
	(314.63,193.29) --
	(315.00,193.41) --
	(315.21,193.48) --
	(315.23,193.49) --
	(315.37,193.53) --
	(315.48,193.57) --
	(315.51,193.58) --
	(315.62,193.62) --
	(315.70,193.64) --
	(315.79,193.67) --
	(316.13,193.79) --
	(316.22,193.82) --
	(316.38,193.87) --
	(316.61,193.95) --
	(316.93,194.05) --
	(317.07,194.10) --
	(317.20,194.14) --
	(317.36,194.20) --
	(317.75,194.33) --
	(317.76,194.33) --
	(317.79,194.34) --
	(317.86,194.36) --
	(317.89,194.37) --
	(317.98,194.40) --
	(318.43,194.55) --
	(318.60,194.61) --
	(318.85,194.69) --
	(319.11,194.78) --
	(319.21,194.81) --
	(319.52,194.91) --
	(319.81,195.01) --
	(320.44,195.22) --
	(321.85,195.69) --
	(321.91,195.71) --
	(322.04,195.75) --
	(322.30,195.84) --
	(322.60,195.94) --
	(322.75,195.99) --
	(323.02,196.08) --
	(323.10,196.10) --
	(323.28,196.16) --
	(324.05,196.42) --
	(324.42,196.54) --
	(324.61,196.60) --
	(324.72,196.64) --
	(325.08,196.76) --
	(325.99,197.06) --
	(326.58,197.26) --
	(326.72,197.31) --
	(327.61,197.60) --
	(327.91,197.70) --
	(328.67,197.95) --
	(328.94,198.04) --
	(329.07,198.09) --
	(329.52,198.24) --
	(331.17,198.78) --
	(332.00,199.06) --
	(332.27,199.15) --
	(333.07,199.42) --
	(333.19,199.45) --
	(333.76,199.64) --
	(335.51,200.23) --
	(336.07,200.41) --
	(336.75,200.64) --
	(336.88,200.68) --
	(337.54,200.90) --
	(337.92,201.03) --
	(338.29,201.15) --
	(338.32,201.16) --
	(338.37,201.17) --
	(338.79,201.32) --
	(338.87,201.34) --
	(339.41,201.52) --
	(339.54,201.56) --
	(340.26,201.80) --
	(340.28,201.81) --
	(340.36,201.84) --
	(340.58,201.91) --
	(340.90,202.02) --
	(341.07,202.07) --
	(341.38,202.18) --
	(341.48,202.21) --
	(341.53,202.23) --
	(341.57,202.24) --
	(342.00,202.38) --
	(342.06,202.40) --
	(342.60,202.58) --
	(342.92,202.69) --
	(344.39,203.18) --
	(344.81,203.31) --
	(345.03,203.39) --
	(345.51,203.55) --
	(345.56,203.56) --
	(346.27,203.80) --
	(348.09,204.40) --
	(348.19,204.44) --
	(348.32,204.48) --
	(348.52,204.55) --
	(348.65,204.59) --
	(350.04,205.05) --
	(350.29,205.13) --
	(350.39,205.17) --
	(351.49,205.53) --
	(354.19,206.43) --
	(354.41,206.50) --
	(354.96,206.69) --
	(354.99,206.69) --
	(355.28,206.79) --
	(355.84,206.98) --
	(356.71,207.27) --
	(356.75,207.28) --
	(357.50,207.53) --
	(357.53,207.54) --
	(358.04,207.71) --
	(358.62,207.90) --
	(359.31,208.13) --
	(359.62,208.23) --
	(359.75,208.28) --
	(359.85,208.31) --
	(360.61,208.56) --
	(360.64,208.57) --
	(360.71,208.60) --
	(361.91,208.99) --
	(362.60,209.22) --
	(364.24,209.77) --
	(364.46,209.84) --
	(365.70,210.25) --
	(366.29,210.45) --
	(370.53,211.86) --
	(371.02,212.02) --
	(372.06,212.37) --
	(372.07,212.37) --
	(372.38,212.47) --
	(372.60,212.54) --
	(372.90,212.65) --
	(373.16,212.73) --
	(373.53,212.86) --
	(373.80,212.94) --
	(374.46,213.16) --
	(374.81,213.28) --
	(375.77,213.60) --
	(376.36,213.80) --
	(376.51,213.85) --
	(376.93,213.98) --
	(378.03,214.35) --
	(379.36,214.79) --
	(379.36,214.79) --
	(380.09,215.03) --
	(380.12,215.04) --
	(381.03,215.35) --
	(381.47,215.49) --
	(381.75,215.58) --
	(382.36,215.79) --
	(382.44,215.82) --
	(382.57,215.86) --
	(383.02,216.01) --
	(385.04,216.68) --
	(385.16,216.72) --
	(388.87,217.95) --
	(393.56,219.51) --
	(395.71,220.22) --
	(403.26,222.73) --
	(404.02,222.98);
\definecolor[named]{fillColor}{rgb}{0.20,0.20,0.20}

\path[fill=fillColor,fill opacity=0.30] ( 52.97,167.36) --
	( 61.01,168.41) --
	( 65.48,168.80) --
	( 65.62,168.81) --
	( 79.64,170.79) --
	( 88.50,171.79) --
	( 94.41,172.49) --
	( 97.84,173.06) --
	(104.50,173.98) --
	(110.01,174.56) --
	(113.94,175.03) --
	(116.56,175.36) --
	(124.94,176.30) --
	(160.01,181.27) --
	(160.15,181.30) --
	(163.56,181.70) --
	(164.50,181.78) --
	(175.08,183.35) --
	(177.68,183.86) --
	(185.12,185.40) --
	(195.04,187.30) --
	(195.05,187.30) --
	(199.79,188.52) --
	(200.09,188.60) --
	(201.70,188.94) --
	(202.42,189.05) --
	(203.15,189.18) --
	(203.24,189.19) --
	(203.92,189.29) --
	(204.08,189.32) --
	(205.70,189.71) --
	(211.30,190.89) --
	(213.02,191.21) --
	(213.22,191.26) --
	(213.28,191.27) --
	(214.88,191.68) --
	(219.39,192.70) --
	(219.87,192.77) --
	(224.51,193.76) --
	(226.38,194.26) --
	(226.89,194.38) --
	(228.22,194.75) --
	(229.80,195.15) --
	(230.53,195.25) --
	(231.54,195.47) --
	(232.29,195.59) --
	(232.55,195.66) --
	(232.60,195.67) --
	(233.03,195.77) --
	(236.50,196.61) --
	(238.44,197.03) --
	(239.50,197.27) --
	(240.76,197.54) --
	(242.87,198.03) --
	(243.82,198.26) --
	(244.87,198.51) --
	(245.90,198.81) --
	(247.14,199.15) --
	(247.15,199.15) --
	(248.00,199.39) --
	(248.59,199.55) --
	(249.15,199.72) --
	(249.91,199.94) --
	(250.14,200.00) --
	(250.71,200.16) --
	(251.21,200.29) --
	(251.61,200.40) --
	(251.88,200.46) --
	(252.52,200.69) --
	(252.98,200.84) --
	(253.12,200.86) --
	(253.36,200.89) --
	(254.91,201.29) --
	(255.02,201.32) --
	(256.32,201.72) --
	(258.61,202.38) --
	(260.03,202.80) --
	(260.14,202.84) --
	(260.80,203.04) --
	(261.97,203.27) --
	(262.19,203.35) --
	(262.48,203.44) --
	(262.99,203.62) --
	(264.29,204.03) --
	(264.50,204.10) --
	(264.53,204.11) --
	(264.97,204.25) --
	(266.10,204.54) --
	(266.13,204.55) --
	(266.44,204.61) --
	(267.28,204.93) --
	(267.71,205.05) --
	(268.38,205.26) --
	(269.11,205.45) --
	(269.74,205.69) --
	(269.87,205.74) --
	(271.02,206.18) --
	(271.10,206.22) --
	(271.68,206.47) --
	(272.40,206.66) --
	(272.79,206.78) --
	(273.63,207.07) --
	(274.52,207.40) --
	(275.28,207.68) --
	(275.59,207.78) --
	(276.13,207.95) --
	(276.31,207.99) --
	(276.77,208.14) --
	(277.30,208.37) --
	(277.98,208.66) --
	(278.04,208.68) --
	(278.45,208.79) --
	(279.17,208.98) --
	(279.30,209.02) --
	(279.52,209.08) --
	(279.66,209.14) --
	(279.69,209.14) --
	(280.15,209.31) --
	(280.53,209.48) --
	(280.72,209.56) --
	(281.20,209.75) --
	(281.36,209.82) --
	(281.45,209.85) --
	(282.80,210.34) --
	(283.05,210.37) --
	(283.89,210.70) --
	(283.98,210.74) --
	(284.07,210.78) --
	(284.62,210.98) --
	(284.86,211.08) --
	(285.03,211.13) --
	(285.13,211.16) --
	(286.00,211.42) --
	(286.57,211.61) --
	(286.59,211.61) --
	(287.25,211.79) --
	(287.81,211.98) --
	(288.54,212.28) --
	(288.59,212.29) --
	(289.22,212.44) --
	(289.76,212.64) --
	(290.76,213.08) --
	(290.86,213.13) --
	(291.20,213.21) --
	(291.32,213.21) --
	(291.81,213.42) --
	(291.88,213.46) --
	(292.21,213.58) --
	(292.36,213.65) --
	(292.42,213.69) --
	(292.49,213.72) --
	(292.51,213.74) --
	(292.62,213.79) --
	(293.21,213.98) --
	(293.91,214.28) --
	(295.25,214.70) --
	(295.45,214.78) --
	(295.51,214.81) --
	(295.93,215.00) --
	(295.99,215.02) --
	(296.10,215.06) --
	(296.47,215.21) --
	(296.65,215.26) --
	(296.99,215.30) --
	(297.01,215.30) --
	(297.04,215.31) --
	(297.05,215.31) --
	(297.09,215.32) --
	(297.13,215.34) --
	(297.22,215.39) --
	(297.31,215.44) --
	(297.31,215.44) --
	(297.71,215.55) --
	(297.96,215.64) --
	(298.34,215.77) --
	(298.57,215.86) --
	(299.04,216.04) --
	(300.58,216.50) --
	(300.69,216.54) --
	(301.32,216.72) --
	(302.10,216.99) --
	(302.23,217.04) --
	(302.50,217.16) --
	(302.82,217.32) --
	(302.98,217.40) --
	(303.49,217.63) --
	(303.87,217.81) --
	(304.04,217.89) --
	(304.05,217.89) --
	(304.17,217.95) --
	(304.21,217.97) --
	(304.88,218.27) --
	(305.44,218.51) --
	(305.52,218.55) --
	(305.61,218.58) --
	(305.86,218.68) --
	(306.19,218.81) --
	(306.32,218.86) --
	(307.91,219.57) --
	(307.96,219.60) --
	(308.47,219.81) --
	(308.57,219.85) --
	(309.22,220.10) --
	(309.44,220.18) --
	(309.51,220.20) --
	(309.67,220.25) --
	(310.00,220.39) --
	(310.25,220.47) --
	(310.76,220.68) --
	(310.92,220.74) --
	(311.04,220.77) --
	(311.16,220.82) --
	(311.41,220.90) --
	(311.41,220.90) --
	(311.44,220.91) --
	(311.54,220.94) --
	(311.68,220.98) --
	(311.68,220.99) --
	(311.88,221.05) --
	(312.22,221.19) --
	(312.92,221.49) --
	(313.12,221.57) --
	(313.27,221.65) --
	(313.53,221.73) --
	(313.83,221.83) --
	(314.24,222.00) --
	(314.31,222.04) --
	(314.45,222.11) --
	(314.63,222.16) --
	(315.00,222.37) --
	(315.21,222.46) --
	(315.23,222.47) --
	(315.37,222.52) --
	(315.48,222.56) --
	(315.51,222.58) --
	(315.62,222.62) --
	(315.70,222.64) --
	(315.79,222.66) --
	(316.13,222.81) --
	(316.22,222.83) --
	(316.38,222.87) --
	(316.61,222.95) --
	(316.93,223.12) --
	(317.07,223.18) --
	(317.20,223.26) --
	(317.36,223.33) --
	(317.75,223.47) --
	(317.76,223.47) --
	(317.79,223.49) --
	(317.86,223.53) --
	(317.89,223.54) --
	(317.98,223.58) --
	(318.43,223.78) --
	(318.60,223.85) --
	(318.85,224.00) --
	(319.11,224.09) --
	(319.21,224.11) --
	(319.52,224.25) --
	(319.81,224.40) --
	(320.44,224.64) --
	(321.85,225.23) --
	(321.91,225.27) --
	(322.04,225.35) --
	(322.30,225.47) --
	(322.60,225.60) --
	(322.75,225.66) --
	(323.02,225.77) --
	(323.10,225.80) --
	(323.28,225.87) --
	(324.05,226.17) --
	(324.42,226.34) --
	(324.61,226.43) --
	(324.72,226.50) --
	(325.08,226.65) --
	(325.99,227.12) --
	(326.58,227.38) --
	(326.72,227.44) --
	(327.61,227.83) --
	(327.91,227.96) --
	(328.67,228.25) --
	(328.94,228.38) --
	(329.07,228.46) --
	(329.52,228.70) --
	(331.17,229.50) --
